From khudian@manchester.ac.uk Thu Sep 22 16:17:13 2016
Date: Thu, 22 Sep 2016 16:17:13 +0100
From: Hovhannes Khudaverdian <khudian@manchester.ac.uk>
To: staff@maths.manchester.ac.uk, postgrads@maths.manchester.ac.uk
Subject: Letter from Hovik Khudaverdian on lectures on Quantum Mechanics.


               Dear colleagues and students
   First of all sorry for the second circular letter.
  I hope this will be the last one:
    I just created the mailing list of people who are interested in the
lectures on Quantum Mechanics (see the copy of the previous letter on 
the 2-nd  September in the end of this letter),
    I have sent already the letter to people in this mailing list.
    Please inform me If there is somebody who is not included in the miling
list (my apologies if this is due to my mistake)  or who 
just decided to be in the list.
   In a few days (when I will know exactly the details of my timetable)
   I will send you three possible slots for the lecture, 
and I will choose the day which is better for majority of you.
   Sure all the next letters will be sent only to the people who are 
interested, i.e. to the mailing list.
   If this will work,
   I hope to begin the lectures during the second week.

                  Hovik




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    This is the letter which was sent at beginning of September:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

              Dear colleagues and dear students,
     There is a project that I have been thinking about for many years and
finally I decided to give it a try:
an experimental course ``Topics in Quantum Mechanics'.
     Over years I have heard from some PhD students that they would like to
learn basics of this subject. Some of them made attempts to attend the
corresponding course in the School of Physics, and these students told
me that it would be nice and more efficient if this course would be
delivered specially to mathematicians.
     I am planning a course oriented towards graduate students in
Mathematics. I plan to give about 8-10 lectures. Many things will depend
on the people who will come to listen the course.
     Below you can see a preliminary version of the programme of the course.
Sure it is a very preliminary version.
         I need to know:
1) how many people approximately  will attend the course
2) your opinion about the programme.
     Those who are interested to attend the course, please respond to this
letter. I will be happy to receive any comments about the programme below.
         After 21 September I will send the letter to fix the day
and time for the course.

                          Hovik
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
                    Topics in Quantum Mechanics
                    H.M.Khudaverdian
    Preliminary programme

         1. Unitary space: complex linear space with Hermitian metric.
Self-adjoint operators in a unitary space. States and observables in
Quantum Mechanics. Measurement: commuting and non-commuting observables.
Cauchy-Bunyakovsky-Schwarz inequality and Heisenberg uncertainty principle.
         2. Wave-function in Quantum Mechanics and action in Classical
Mechanics. Schroedinger equation. Coordinate and momentum
representations. Harmonic oscillator.
         3. Rotation and angular momentum. Spin of a particle.
         4. Perturbation theory: abrupt and adiabatic perturbations.
Adiabatic invariants in Quantum Mechanics and in Classical Mechanics.
         5. Quasiclassical approximation in Quantum Mechanics and
Hamilton-Jacobi equation in Classical Mechanics. Fourier transform and
Legendre transform. Maslov index.
         6. Elements of Quantum Logic. Modular lattice of questions
in Quantum Mechanics and distributive lattice of
questions in  Classical Mechanics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



                                       Dr Hovhannes Khudaverdian
                                       The University of Manchester
                                          School of Mathematics
                                      e-mail: khudian@manchester.ac.uk
                                           tel. 0161-2008975
