

     Zdravstvujte, Jura
  Ja v dekare poslal Marku zajavku na kurs:;
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  GRADUATE COURSE FOR PHD STUDENTS
Elements of Quantum Mechanics for mathematicians

This course counts as 33 hours of the taught component 
of a PGR programme.

{\bf Total Time: 22 lectures over 11 weeks
 ( $+$ up to 11 tutorial sessions) Academic Year: 2018/2019
Course leader: Hovhannes Khudaverdyan

   ....................
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  Daljshe sledujet opisanije kursa, syllabus, i.t.d. sootvetstvenno
  obraztsu (sm. attachment)


    V otvetnom pisjme  Mark napisal mne:


*************************************************************
Dear Hovik,

I sent it to Matthias (who needs to approve it to count towards the taught 
course requirement for PhD students) and he asked for the "up to 11 
tutorial sessions" to be made more specific (I would personally suggest 
just "11 tutorial session"!) and for a bit more detail about the 
assignments:
> Can we change the "up to 11 tutorial sessions" to something more 
> specific, and provide some more detail about the nature of the assignments?
Could you please edit slightly to address these and let me have a revised 
PDF?
Thanks! Mark
***************************************************************

Ja sobirajusj v otvetnom pisjme zamenitj

"up to 11 tutorial sessions"  na 

 " to 11 tutorial sessions" 

  i napisatj about assignments the following:

   During every lecture  it will be suggested exercises,
 the solution of these exercises will be discussed during
totirals.  In addition during lecture course it will be given
two assignments  (after fifth and tenth week). Every assigmnent
will contain about 5-6 problems, Students have to hand the
solutions of these assignments, they will be discussed later on tutorials.


   Yura menia nemnogo pugajut formaljnoje trebovanije k tutorialam.
Ja v printsipe konehcno khocu delaj lektsii po dva chassa
i organizovatj shto-to tipa office hours-- 
dva dnia v nedelju po chassu dva --eto mozhet bytj zamena tutorilo  
